---
  title: 'Random Survival Forest Model'
---
  
---

# Initialization 

In the second example, we present the Random Forest model for a distance measure approximation applied on the `ovarian` data set from the `survival` package. This package offers two ways for distance/similarity calculation (see documentation): 

- proximity

- pathway 

Let's initialize the R6 data object. 

<br>
```{r, warning=FALSE, message=FALSE}
library(survival)
library(cbr)
ovarian$resid.ds <- factor(ovarian$resid.ds)
ovarian$rx <- factor(ovarian$rx)
ovarian$ecog.ps <- factor(ovarian$ecog.ps)

# initialize R6 object
sc <- cbrRFProxy$new(learning=ovarian, verumData=ovarian, learnVars=c("age", "resid.ds", "rx", "ecog.ps"), endPoint=c("futime", "fustat"), impute=T)
```
If `impute` is set to `FALSE` (for the Cox model the `ìmpute` variable is always set to `FALSE`) then all cases with missing values in the learning and end point variables are dropped (`na.omit`) and the reduced data set without missing values is saved internally. You get a text output on how many cases were dropped. The variables should be `numeric` or `factor`. `character` variables will be transformed to `factor`.


# Learning RandomForest

Optionally, you may want to adjust some parameters in the fitting step of the random forest algorithm. Possible arguments are: `nCores`, `ntree`, `mtry`, `splitrule`, `ntime`, `nsplit`, and `verbose`. The documentation of this parameters can be found in the randomForestSRC R-package.

```{r}
sc$learn()
```

All other steps (excluding checking for linearity and proportional hazard assumption are the same as for the Cox-model).

<br>
