---
  title: 'RandomForest Proximity Model'
---
  
---

# Initialization 

In the second example, we present the RandomForest Proximity matrix as distance measure and the `ovarian` data set from the `survival` package. In the first step we initialize the R6 data object. The initialization needs several inputs:
  
**Arguments:**
  
  ------------------------ | ----
*learning*       | data set for learning the RandomForest
*verumData* | Verum data set. For each case in the verum data, we are looking for the m (=1,...,k) similar cases. Learning and verum data set need the same structure (variable names and scales)
*learnVars (optional)* | A character vector variable names. This variables are used for learning the model. Do not include time2event and event variable here. Default: all variables, except endPoint variables, are used for model fitting.
*endPoint (optional)* | A character vector of length two. The first elements contains the variable name of the time 2 event variable and the second the name of the event variable. Default: ` c("Time2Event", "Event")`
*impute (optional)* | TRUE/FALSE: Missing value imputation (see randomForestSRC-Package for documentation. 

<br>
```{r, warning=FALSE, message=FALSE}
library(survival)
library(cbr)
ovarian$resid.ds <- factor(ovarian$resid.ds)
ovarian$rx <- factor(ovarian$rx)
ovarian$ecog.ps <- factor(ovarian$ecog.ps)

# initialize R6 object
sc <- cbrRFProxy$new(learning=ovarian, verumData=ovarian, learnVars=c("age", "resid.ds", "rx", "ecog.ps"), endPoint=c("futime", "fustat"), impute=T)
```
If `impute` is set to `FALSE` (for the Cox model the `ìmpute` variable is always set to `FALSE`) then all cases with missing values in the learning and end point variables are dropped (`na.omit`) and the reduced data set without missing values is saved internally. You get a text output on how many cases were dropped. The variables should be `numeric`
 or `factor`.

# Learning RandomForest

Optionally, you may want to adjust some parameters in the fitting step of the random forest algorithm. Possible arguments are: `nCores`, `ntree`, `mtry`, `splitrule`, `ntime`, `nsplit`, and `verbose`. The documentation of this parameters can be found in the randomForestSRC R-package.

```{r}
sc$learn()
```

All other steps (excluding checking for linearity and proportional hazard assumption are the same as for the Cox-model).

<br>
