---
  title: 'Workflow'
---
  
---

**Note:** Package is in active development. Structure, workflow, and syntax may change dramatically.

Following diagramm describes the workflow of the case-based reasoning R package. Box colour has different meanings:

- <span style="color:#2773ae">Useable:</span> this features can be used
- <span style="color:#990000">Not useable: </span> planned features
- <span style="color:#507E4E">Optional:</span> this function will be called by subsequent features and can be called optionally; this means, if you call e.g. call 'Calculate Distance Matrix' automatically the node 'Modell Fitting' will be called (if not already done!)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(DiagrammeR)
```

```{r, eval=TRUE, echo=FALSE}
DiagrammeR("
  graph TB
    A[Initialize CBR Object]
    B[Variable Selection]
    C[Model Fitting]
    D[Check Proportional Hazard]
    E[Calculate Distance Matrix];
    F[Get Similar Cases];
    H[Extract Data]
    
    A-->|Cox-Model<br>-optional-|B;
    A-->C;
    B-->C;
    C-->|Cox-Model<br>-optional-|D;
    C-->E;
    E-->F;
    F-->H;

    style A fill:#fff, stroke:#2773ae, stroke-width:2px;
    style B fill:#fff, stroke:#2773ae, stroke-width:2px;
    style C fill:#fff, stroke:#507E4E, stroke-width:2px;
    style D fill:#fff, stroke:#2773ae, stroke-width:2px;
    style E fill:#fff, stroke:#507E4E, stroke-width:2px;
    style F fill:#fff, stroke:#2773ae, stroke-width:2px;
    style H fill:#fff, stroke:#2773ae, stroke-width:2px;
")
```
