```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(DiagrammeR)
```

# Class Structure

**Note:** Package is in active development. Structure, workflow, and sytax may change dramatically.

Following diagramm describes the workflow of the case-based reasoning R package. Box colour has different meanings:

- <span style="color:#2773ae">Useable:</span> this features can be used
- <span style="color:#990000">Not useable: </span> planned features
- <span style="color:#507E4E">Optional:</span> this function will be called by subsequent features and can be called optionally


```{r, eval=TRUE, echo=FALSE}
DiagrammeR("
  graph TB;
    B-->C[Validate]
    B-->D[Extract Data]
    E[Calculate Full Distance Matrix]
    E-->F[Manifold Learning]
    H-->|Cox-Model<br>-optional-|G[Check Linearity & Proportional Hazard]
    G-->B[Calculate Similar Cases]
    G-->E
    B-->|<strong><span style='color:#990000'> not working</span></strong>|F
    A[Initialize CBR Object]-->I[Variable Selection]
    A-->H
    I-->H[Learn Final Model]
    H-->B
    H-->E;
    
    style A fill:#fff, stroke:#2773ae, stroke-width:2px, color:#ffffff;
    style B fill:#fff, stroke:#2773ae, stroke-width:2px;
    style C fill:#fff, stroke:#2773ae, stroke-width:2px;
    style D fill:#fff, stroke:#2773ae, stroke-width:2px;
    style E fill:#fff, stroke:#2773ae, stroke-width:2px;
    style F fill:#fff, stroke:#2773ae, stroke-width:2px;
    style G fill:#fff, stroke:#2773ae, stroke-width:2px;
    style H fill:#fff, stroke:#507E4E, stroke-width:2px;
    style I fill:#fff, stroke:#990000, stroke-width:2px;
")
```




